---
title: "Creating and Working with Vectors"
author: "Michelle Lam"
date: "2022-08-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(palmerpenguins)
```

To back your R project on Github and create version control, create your project, in the console run the command usethis::use_git() to create your local repo, to set up the remote repo run the command usethis::use_github() in the console.

To pull a repo from Github into your local environment, Fork the repo in Github and then click the Clone button (copy the URL), create a project in R and select version control, select Git, paste in the copied URL and create your project

### Make Some Vectors

```{r}
# You can normally use double or single quotes interchangeably
# Can't have varying classes in a single vector
marmots <- c("blue", "green", 4, "yellow")

# Check class
class(marmots)
```


```{r}
pika <- c(12.4, 6.8, 2.9, 8.8, 8.5)
class(pika)

# Scalar multiplier

scalar_pika <- 5.2 * pika

# To show data in knit call the value in the code
scalar_pika
```

```{r}
bananas <- c(1,2,3)
apples <- c(6,7,8)

# Adding and subtracting vectors
bananas + apples
bananas - apples

# calculate the dot product in R
bananas %*% apples
```

### Matrices

```{r}
my_values <- seq(from = 1, to = 10)
# use by as the third variable to set number of values in sequence

my_matrix <- matrix(data = my_values, nrow = 2, ncol = 5, byrow = TRUE)
my_matrix

5 * my_matrix
```

```{r}
glimpse(penguins)
```

In Terminal tab type in pwd print working directory to see where you are
git status will show you what's been changed
Terminal communicates with computer, console communicates with R
